Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-09 journal paper/content/related_work.tex
Added a comment.
Added a para on "greedy".

\xhdr{Bandits and exploration.} Multi-armed bandits (\emph{MAB}) is a particularly elegant and tractable abstraction for tradeoff between \emph{exploration} and \emph{exploitation}: essentially, between acquisition and usage of information. MAB problems have been studied in Economics, Operations Research and Computer Science for many decades, \asedit{and are covered in many books and surveys. Particularly, see
\citet{Bubeck-survey12,slivkins-MABbook,LS19bandit-book} for background on regret-minimizing formulations of bandits, \citet{Gittins-book11} for Bayesian and Markovian formulations, and \citet{CesaBL-book,slivkins-MABbook} for connections to economics and game theory.} A discussion of industrial applications of MAB can be found in \citep{DS-arxiv} and \citep[Ch. 8]{slivkins-MABbook}.

@@

@@

>>>>

\xhdr{Bandits and exploration.} Multi-armed bandits (\emph{MAB}) is a particularly elegant and tractable abstraction for tradeoff between \emph{exploration} and \emph{exploitation}: essentially, between acquisition and usage of information. MAB problems have been studied in Economics, Operations Research and Computer Science for many decades, \asedit{and are covered in many books and surveys. Particularly, see
\citet{Bubeck-survey12,slivkins-MABbook,LS19bandit-book} for background on regret-minimizing formulations of bandits, \citet{Gittins-book11} for Bayesian and Markovian formulations, and \citet{CesaBL-book,slivkins-MABbook} for connections to economics and game theory.}

@@

\asedit{The greedy algorithm is terrible on a wide variety of problem instances, in the sense that it fails to try the best arm and therefore suffers regret linear in the time horizon  
\citep[see Chapter 11.2 in][]{slivkins-MABbook}. 
On the other hand, a recent line of work \citep{kannan2018smoothed,bastani2017exploiting,externalities-colt18}
finds that the greedy algorithm performs well (in theory), in a model of linear contextual bandits under substantial assumptions on smoothing or heterogeneity of the context vectors.}

A discussion of industrial applications of MAB can be found in \citep{DS-arxiv} and \citep[Chapter 8]{slivkins-MABbook}. \asedit{In particular, switching from ``greedy" to ``exploration-separating" to ``adaptive-exploration" algorithms involves substantial adoption costs in infrastructure and personnel training.}

@@

\ascomment{Guy: In EC20 you cited \cite{kerin1992first} for a survey on first-mover advantage. Why not now? Likewise, you also had a para on Lerner Inder and such (last para in related work in EC20).}
